\chapter{Conclusion}

This projected consisted on the development of a 

\section{Future development}

As this project represents a final bachelor's project, some future work could still be done in order
to publish and deploy the platform to the general public, making it more successful and profitable.\\

Here are some topics the group agreed that could belong to this project's future development:

\subsubsection{Statistics analysis}

Given that one of this project's main strengths is information storage and mapping, the group found
relevant that statistics analysis should be done, in order to help and provide other work fields
information that could be useful.\\

However every data that is collected should be properly disclaimed and only the information that
would not compromised the user's privacy should be colectable.

\subsubsection{Interaction with similar platforms}

As written in the last topic, the information could enrich the world of nutrition and health platforms.
To allow this, the API could be available to the public, so it could be integrated with other platforms
alike.\\

\subsubsection{Improved social system}

This platform depends strongly on the community, as such there should be a social system improval in order
to make its members more active and the platform's more responsive and fulfilled.\\

One way to do that could be social rewards for the most active and contributive users.

\subsubsection{Client UI/UX revision}

The user interface should be reviewed and improved by an UI/UX team which has the tools to make the clients' 
interface more appealing to the users.

\subsubsection{Certified members}

Anyone can participate and make submissions to the platform. Given this fact, voided information
can be submitted and spread inside the community, contributing to misinformation.\\

To tackle this issue there should be member certifications for the most active members or even
certified professionals, which could validate submitted information and make the platform's
environment a more trustworthy place online.

\subsubsection{Two-factor authentication}

Security is a very important topic nowadays, being a field that is constantly evolving. As it is proven
that single-factor authentication might be not enough to avoid attacks completely, a two-factor authentication
could be implemented to improve user's security.

